Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-26 ltx/data_paper/DataPaper.tex
edits to conclusion

\section{Conclusion}
In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data, where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.  It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified. This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process. In addition to the connectivity kernel weights and the synaptic parameter, the observation noise and disturbance variances were also identified. The empirical distributions of the estimated non-kernel parameters showed small bias with very small standard deviations.

>>>>

\section{Conclusion}
In this chapter, a method has been developed to estimate the states and parameters of a spatially continuous neural field model from electrophysiological data. The novel aspects of this chapter include an estimator for the kernel spatial support and the field disturbance characteristics. The derivations and computational results demonstrate that by choosing the synaptic time constant and the observation noise variance within a plausible range, the unknown supports can be identified. The inclusion of this step facilitates the use of the EM algorithm, where the complexity is decreased and the accuracy is improved by reducing the number of unknown variables. In addition to the connectivity kernel weights and the synaptic parameter, the observation noise and disturbance variances were identified. The results using simulated data demonstrated good estimation performance, where the distributions of the estimated non-kernel parameters showed small bias with very small standard deviations.

The data-driven modelling framework presented in this chapter provides a much needed link between theoretical and experimental neuroscience. By establishing this link, patient-specific systems neuroscience may eventually be used in a clinical setting, which has the potential to revolutionise  neurosciences and neurology.
